\problemname{Cookie Game}

\noindent Gustav and Oskar found some cookies in
\href{https://wiki.dtek.se/wiki/Basen}{the base}, so they put them in a line on
the table and numbered them $1$ to $n$ from left to right.  Cookie number $i$
takes $a_i$ bites to eat. Gustav and Oskar want to eat the cookies, but they
couldn't agree on how to divide the cookies between themselves, so they decided
to play a game. They will take turns playing a move. A move consists of either

\begin{itemize}
  \item taking a cookie from the table, or
  \item taking a bite from a previously taken cookie
\end{itemize}

\noindent If Gustav or Oskar take a cookie, they must finish eating it before
taking another one.  When there are no cookies left and one player has finished
his last cookie, he has to wait while the other player finishes his.

Oskar's strategy is to always take the leftmost cookie (lowest index) when he
can take a new cookie.  Gustav makes the first move and wants to eat as many
cookies as possible. How many cookies can he eat if he knows about Oskar's
strategy and plays optimally?

\section*{Input}
The first line contains the integer $n$.  The second line contains the $n$ space
separated integers $a_i$ ($1 \leq a_i$).

\section*{Output}
Output one integer, the maximum number of cookies Gustav can get.

\section*{Scoring}

\noindent
\begin{tabular}{| l | l | l |}
\hline
Group & Points     & Constraints \\ \hline
$1$   & $25$       & $n \leq 20, a_i \leq 20$ \\ \hline
$2$   & $20$       & $n \leq 75, a_i \leq 75$ \\ \hline
$3$   & $15$       & $n \leq 250, a_i \leq 10^9$ \\ \hline
$4$   & $40$       & $n \leq 5000, a_i \leq 10^9$ \\ \hline
\end{tabular}
